\section{conclusions}\label{concl.sec}

Deep inelastic scattering from $^{1,2}$H, $^{3,4}$He, Be, C, Cu, and Au solid
targets was measured by the E03-103 experiment at the Jefferson Lab. The
ratios of inclusive nuclear cross sections with respect to the deuterium cross
section have been determined for $x>0.3$ for $Q^2$ values between 3 and 8
GeV$^2$.

\textit{no sign of modified x-dependence for light nuclei, but clear deviations
from commonly assumed A and rho dependence}. 

E03-103 experiment addressed some of the limitations in previous measurements
of the EMC effect. The measurement provided benchmark data for calculations of
the EMC effect in light nuclei.  No deviations from the $x$ dependence observed
in heavy nuclei was found for $A=3,4$, but clear deviations from the simple
assumption of mass or density scaling of the EMC effect are seen.  At large x,
where binding and Fermi motion effects dominate, our new data for light and
heavy nuclei can serve as a base-line for traditional nuclear physics
calculations, including several few-body nuclei where structure related
uncertainties are minimal. The data presented in this work will bridge the gap
between measurement of the EMC effect in light nuclei and medium heavy nuclei,
thus providing a comprehensive basis to test state of the art models that
attempt to explain the observed nuclear dependence.  For the moment, few
models provide an explicit prediction for the A dependence, thus limiting the
ability to directly constrain these models without further effort on the
theory side.

While these data provide important new information about the EMC effect, there
are still limitations on how well these results could be used to constrain
explanations of the EMC effect. Some of these limitations will be addressed by
the 12 GeV experiment at Jefferson Lab~\cite{e12008_proposal}. This will
provide further information on the detailed behavior of the observed nuclear
nuclear dependence with an expanded set of light nuclei, including nuclei with
significant cluster structure.

OTHER 12 GeV experiments: off-shell DIS, off-shell FFs, EMC/SRC for 
3H/3He, 40Ca/48Ca, A-dep of R, etc...


